Hierarchical wrinkling in a confined permeable biogel

### 2015-01-26 fig_plis/article_plis.tex
Amplitude dépendante du temps dans un deuxième temps

Yet, in a biological context, thin tissues, e.g. epithelimum or endothelium, are naturally confined and immersed in a nearly buoyant medium, e.g. lymph, blood or mucus, a practical situation were a thin viscous substrate would set the wrinkling wavelength. Moreover, most biological films are porous, and little is known on the interplay between permeability and wrinkling~\cite{Ma2004,Longley2013}. Therefore benchmark experiments that explore the possibility of wrinkling in confined porous soft materials immersed in a buoyancy-matched viscous medium are in line to get fundamental insights into such a biologically relevant situation.

@@

We assume that the deflection can be decomposed in exponentially growing sinusoidal modes and we consider one of them $w(x,t) =  A_0 e^{t/\tau} \sin qx$ of characteristic time $\tau$ and wavevector $q$. Eq.~(\ref{eq:mecheq}) then reads
\begin{equation}
\left(\frac{1}{12} B h^3 q^4 - \sigma_\parallel h q^2\right)w = \sigma_\perp,
\label{eq:mecheqop}
\end{equation}
where $B=E/(1-\nu^2)$ is the modulus of the plate.

@@

Mass conservation writes
\begin{equation}
\frac{\partial Q}{\partial x} + \frac{\partial w}{\partial t} = 0.
\label{eq:conservation}
\end{equation}
Keeping only linear order terms, one gets
\begin{equation}
\frac{12\eta}{\tau} \frac{w}{H^3q^2} = -\sigma_\perp.
\label{eq:PoiseuilleLoad}
\end{equation}

>>>>

Yet, in a biological context, thin tissues, e.g. epithelimum or endothelium, are naturally confined and immersed in a nearly buoyant medium, e.g. lymph, blood or mucus, a practical situation where a thin viscous substrate would set the wrinkling wavelength. Moreover, most biological films are porous, and little is known on the interplay between permeability and wrinkling~\cite{Ma2004,Longley2013}. Therefore benchmark experiments that explore the possibility of wrinkling in confined porous soft materials immersed in a buoyancy-matched viscous medium are in line to get fundamental insights into such a biologically relevant situation.

@@

We decomposed the deflection in sinusoidal modes $w(x,t) =  A \sin qx$ of wavevector $q$. Eq.~(\ref{eq:mecheq}) then reads
\begin{equation}
\left(\frac{1}{12} B h^3 q^4 - \sigma_\parallel h q^2\right)w = \sigma_\perp,
\label{eq:mecheqop}
\end{equation}
where $B=E/(1-\nu^2)$ is the modulus of the plate.

@@

Mass conservation writes
\begin{equation}
\frac{\partial Q}{\partial x} + \frac{\partial w}{\partial t} = 0.
\label{eq:conservation}
\end{equation}

Assuming an exponentially growing amplitude $A(t) = A_0 \exp(t/\tau)$ and keeping only linear order terms, one gets
\begin{equation}
\frac{12\eta}{\tau} \frac{w}{H^3q^2} = -\sigma_\perp.
\label{eq:PoiseuilleLoad}
\end{equation}
